---
title: "Network Analysis"
author: "Asaf Eliyahu & Einat Edelstien"
date: "April 13, 2016"
output: html_document
---

```{r setup, include=FALSE}
library(igraph) 
ga.data <- read.csv('ga_edgelist.csv', header=TRUE) 
g <- graph.data.frame(ga.data, directed=FALSE) 

library(twitteR)
library(tm)
library(plyr)
library(ggplot2)
consumerKey <- 'd9Ie2YnVqLCJQZInCe59iEd7G'
consumerSecret <- 'j7Hjsz4Lza7D8MyrlkpPiSAA9Vtxu0fp0bCBRZa186Hw0jyIBa'
accessToken <- '718353560489095168-YtKnMnbcpPnvWH6du6SDhdtS9ecbHg9'
accessTokenSecret <- 'REOHKpbejvg6si5jXNJDffEbCLrRc9i9oaOv3X5FpWRoL'
twitteR::setup_twitter_oauth(consumerKey,consumerSecret,accessToken,accessTokenSecret)
```

## Part 1 - Grey's Anatomy Network Analysis

```{r , echo=FALSE}
g$layout <- layout.fruchterman.reingold(g) 
plot(g)
#V(g)$label <- NA # remove labels
V(g)$size <- degree(g) * 2 # multiply by 2 for scale 
```

### Betweenness

The vertex with higest betweenness centrality is **Sloan - 115.3667**

```{r , echo=FALSE}
btw <- betweenness(g)
btw.score <- round(btw) + 1 
btw.colors <- rev(heat.colors(max(btw.score))) 
V(g)$color <- btw.colors[ btw.score ] 
plot(g)
btw
max(btw)
```

### Closeness

The vertex with higest closeness centrality is **torres - 0.003194888**

```{r , echo=FALSE}
clo <- closeness(g) 
clo.score <- round( (clo - min(clo)) * length(clo) / max(clo) ) + 1 
clo.colors <- rev(heat.colors(max(clo.score))) 
V(g)$color <- clo.colors[ clo.score ] 
plot(g)
clo
max(clo) #torres - 0.003194888
```

### Eigenvector

The vertex with higest eigenvector centrality is **karev - 1**

```{r , echo=FALSE}
evc <- evcent(g)
evc.score <- round(evc$value) + 1 
evc.colors <- rev(heat.colors(max(evc.score))) 
V(g)$color <- evc.colors[ evc.score ] 
plot(g)
evc$vector
max(evc$vector)
```



###Community structure detection

#### Community strucure via short random walks
```{r , echo=FALSE}
fc <- walktrap.community(g)
memb <- cutat(fc, steps = 5)
memb
sizes(fc)
layout1 <- layout.fruchterman.reingold(g)
plot(g, layout=layout1, vertex.color=memb+1, asp=FALSE)
```

The modularity of the community structure of a graph is 

```{r , echo=FALSE}
fc$modularity
max(fc$modularity)
```

#### Girvan-Newman community detection algorithm
```{r , echo=FALSE}
fc <- edge.betweenness.community(g)
memb <- cutat(fc, steps = 5)
memb
sizes(fc)
plot(g, layout=layout1, vertex.color=memb+1, asp=FALSE)
```

The modularity of the community structure of a graph is 

```{r , echo=FALSE}
fc$modularity
max(fc$modularity)
```
<br /><br />

## Part 2 - Java Network Analysis
For part 2 we choose web crawling and used a Twitter text data collected
from tweets about JAVA.

Here is the code we used for crawling and to build the document-term matrix.
We then plotted the graph to show the relationship between
frequent terms.

```{r , echo=TRUE}
programmingTwitts <- searchTwitter('java', n = 5, lang = 'en', resultType = "popular")

programmingTwitts_text <- sapply(programmingTwitts, function(x) x$getText())

programmingTwitts_text <- gsub("(f|ht)tp(s?)://(.*)[.][a-z]+", "", programmingTwitts_text)
programmingTwitts_text <- gsub(" /.+$", "", programmingTwitts_text)
programmingTwitts_text <- gsub(" @.+ ", "", programmingTwitts_text)
programmingTwitts_corpus <- Corpus(VectorSource(programmingTwitts_text))

programmingTwitts_corpus_clean <- tm_map(programmingTwitts_corpus, removePunctuation)
programmingTwitts_corpus_clean <- tm_map(programmingTwitts_corpus_clean, removeWords, stopwords("english"))
programmingTwitts_corpus_clean <- tm_map(programmingTwitts_corpus_clean, removeWords, c("the","a","http", "via", "you", "are", "an", "also", "however", "may", "this"))
programmingTwitts_corpus_clean <- tm_map(programmingTwitts_corpus_clean, removeNumbers)
programmingTwitts_corpus_clean <- tm_map(programmingTwitts_corpus_clean, stripWhitespace)

tdm <- TermDocumentMatrix(programmingTwitts_corpus_clean)

tdm1 <- tdm

tm <- as.matrix(tdm1)

tdm2 <- tm %*% t(tm)

g <- graph.adjacency(tdm2, weighted=T, mode="undirected")

plot(g)

#vcount(g)
#ecount(g)

g <- simplify(g)


V(g)$label <- V(g)$name
V(g)$degree <- degree(g)
set.seed(3952)
layout1 <- layout.fruchterman.reingold(g)

V(g)$label.cex <- 2.2* V(g)$degree / max(V(g)$degree) + .2
V(g)$label.color <- rgb(0, 0, .2, .8)
V(g)$frame.color <- NA

egam <- (log(E(g)$weight)+.4) / max(log(E(g)$weight)+.4)
E(g)$color <- rgb(.5, .5, 0, egam)
E(g)$width <- egam

```


### Betweenness

The vertex with higest betweenness centrality is **Java - 615**

```{r , echo=FALSE}
btw <- betweenness(g)
btw.score <- round(btw) + 1 
btw.colors <- rev(heat.colors(max(btw.score))) 
V(g)$color <- btw.colors[ btw.score ] 
plot(g)
btw
max(btw)
```

### Closeness

The vertex with higest closeness centrality is **Java - 0.02040816**

```{r , echo=FALSE}
clo <- closeness(g) 
clo.score <- round( (clo - min(clo)) * length(clo) / max(clo) ) + 1 
clo.colors <- rev(heat.colors(max(clo.score))) 
V(g)$color <- clo.colors[ clo.score ] 
plot(g)
clo
max(clo) 
```

### Eigenvector

The vertex with higest eigenvector centrality is **Java - 1**

```{r , echo=FALSE}
evc <- evcent(g)
evc.score <- round(evc$value) + 1 
evc.colors <- rev(heat.colors(max(evc.score))) 
V(g)$color <- evc.colors[ evc.score ] 
plot(g)
evc$vector
max(evc$vector)
```


###Community structure detection

#### Community strucure via short random walks
```{r , echo=FALSE}
fc <- fc <- walktrap.community(g)
memb <- cutat(fc, steps = 5)
memb
sizes(fc)
plot(g, layout=layout1, vertex.color=memb+1, asp=FALSE)
```

The modularity of the community structure of a graph is 

```{r , echo=FALSE}
fc$modularity
max(fc$modularity)
```


#### Girvan-Newman community detection algorithm
```{r , echo=FALSE}
fc <- edge.betweenness.community(g)
memb <- cutat(fc, steps = 5)
memb
sizes(fc)
plot(g, layout=layout1, vertex.color=memb+1, asp=FALSE)
```

The modularity of the community structure of a graph is 

```{r , echo=FALSE}
fc$modularity
max(fc$modularity)
```


#### Community structure via greedy optimization of modularity
```{r , echo=FALSE}
fc <-  fastgreedy.community(g)
memb <- cutat(fc, steps = 5)
memb
sizes(fc)
plot(g, layout=layout1, vertex.color=memb+1, asp=FALSE)
```

The modularity of the community structure of a graph is 

```{r , echo=FALSE}
fc$modularity
max(fc$modularity)
```



